Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-19 hscc2017/paper.tex
font
comma

Each iteration of the loop adds a new input to the finite set $\text{\sc
inputs}$ that is used for synthesis.  Given that the full set of inputs
$\mathcal{D}$ is finite, this means that the refinement loop can only
iterate a potentially very large, but finite number of times.

@@

% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
Next, the following matrix
$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right), 
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
We have that~\cite{astrom1997computer} 
$S(z)$ is the
characteristic polynomial of a stable system if and only if the following four conditions hold:
%\begin{itemize}
%\item 
$R_1: S(1) > 0$;
%\item 
$R_2: (−1)^N S(−1) > 0$;
%\item 
$R_3: |a_0| < a_N$;
%\item 
$R_4: m_{11} > 0 \wedge\allowbreak
      m_{31}>0 \wedge\allowbreak
      m_{51}>0 \wedge \ldots \wedge\allowbreak
      m_{(2N{-}3)(1)}>0$.
%\end{itemize}
%
The stability property is then encoded by a constraint of the form:
$
\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}

>>>>

Each iteration of the loop adds a new input to the finite set $\text{\sc
inputs}$ that is used for synthesis.  Given that the full set of inputs
$\mathcal{D}$ is finite, this means that the refinement loop can only
iterate a potentially very large but finite number of times.

@@

% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
Next, the following matrix
$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right), 
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \mbox{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\mbox{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
\end{array}
\right.
$$
%
and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
We have that~\cite{astrom1997computer} 
$S(z)$ is the
characteristic polynomial of a stable system if and only if the following four conditions hold:
%\begin{itemize}
%\item 
$R_1: S(1) > 0$;
%\item 
$R_2: (−1)^N S(−1) > 0$;
%\item 
$R_3: |a_0| < a_N$;
%\item 
$R_4: m_{11} > 0 \wedge\allowbreak
      m_{31}>0 \wedge\allowbreak
      m_{51}>0 \wedge \ldots \wedge\allowbreak
      m_{(2N{-}3)(1)}>0$.
%\end{itemize}
%
The stability property is then encoded by a constraint of the form:
$
\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}
